Molecular Analysis

### 2023-06-20 analysis/epi_analysis.Rmd
minor update of results

```{r}
est_res <- summary(latInfMod, probs = c(0.025, 0.975), pars = c("phi", "alpha", "omega", "beta", "vega", "mu_p_in", "sigma_p_in"))$summary %>%
  data.frame() %>%
  add_rownames() %>%
  rename(variable = rowname) %>%
  mutate(variable = c("$\\phi$",
                      "$\\alpha$",
                      "$\\omega$",
                      "$\\beta_1$",
                      "$\\beta_2$",
                      "$\\beta_3$",
                      "$\\beta_4$",
                      "$\\beta_5$",
                      "$\\beta_6$",
                      "$\\vega_{\\text{Saturday}}$",
                      "$\\vega_{\\text{Sunday}}$",
                      "$\\vega_{\\text{Monday}}$",
                      "$\\vega_{\\text{Tuesday}}$",
                      "$\\vega_{\\text{Wednesday}}$",
                      "$\\vega_{\\text{Thursday}}$",
                      "$\\vega_{\\text{Friday}}$",
                      "$\\mu_{p_{\\text{IN}}^{\\text{Flu B}}}",
                      "$\\mu_{p_{\\text{IN}}^{\\text{HRV}}}",
                      "$\\mu_{p_{\\text{IN}}^{\\text{AdV}}}",
                      "$\\mu_{p_{\\text{IN}}^{\\text{CoV}}}",
                      "$\\mu_{p_{\\text{IN}}^{\\text{MPV}}}",
                      "$\\mu_{p_{\\text{IN}}^{\\text{PIV}}}",
                      "$\\sigma_{p_{\\text{IN}}^{\\text{Flu B}}}",
                      "$\\sigma_{p_{\\text{IN}}^{\\text{HRV}}}",
                      "$\\sigma_{p_{\\text{IN}}^{\\text{AdV}}}",
                      "$\\sigma_{p_{\\text{IN}}^{\\text{CoV}}}",
                      "$\\sigma_{p_{\\text{IN}}^{\\text{MPV}}}",
                      "$\\sigma_{p_{\\text{IN}}^{\\text{PIV}}}")) %>%
  dplyr::select(variable, mean, `X2.5.`, `X97.5.`, n_eff, Rhat) %>%
  mutate(across(c(mean, `X2.5.`, `X97.5.`), function(x) tex_sign(round_k(x)))) %>%
  as.matrix()

>>>>

```{r}
est_res <- summary(latInfMod, probs = c(0.025, 0.975), pars = c("phi", "alpha", "omega", "beta", "vega", "mu_p_in", "sigma_p_in"))$summary %>%
  data.frame() %>%
  add_rownames() %>%
  rename(variable = rowname) %>%
  mutate(variable = c("$\\phi$",
                      "$\\alpha$",
                      "$\\omega$",
                      "$\\beta_1$",
                      "$\\beta_2$",
                      "$\\beta_3$",
                      "$\\beta_4$",
                      "$\\beta_5$",
                      "$\\beta_6$",
                      "$\\vega_{\\text{Saturday}}$",
                      "$\\vega_{\\text{Sunday}}$",
                      "$\\vega_{\\text{Monday}}$",
                      "$\\vega_{\\text{Tuesday}}$",
                      "$\\vega_{\\text{Wednesday}}$",
                      "$\\vega_{\\text{Thursday}}$",
                      "$\\vega_{\\text{Friday}}$",
                      "$\\mu_{p_{\\text{IN}}^{\\text{Flu B}}}",
                      "$\\mu_{p_{\\text{IN}}^{\\text{HRV}}}",
                      "$\\mu_{p_{\\text{IN}}^{\\text{AdV}}}",
                      "$\\mu_{p_{\\text{IN}}^{\\text{CoV}}}",
                      "$\\mu_{p_{\\text{IN}}^{\\text{MPV}}}",
                      "$\\mu_{p_{\\text{IN}}^{\\text{PIV}}}",
                      "$\\sigma_{p_{\\text{IN}}^{\\text{Flu B}}}",
                      "$\\sigma_{p_{\\text{IN}}^{\\text{HRV}}}",
                      "$\\sigma_{p_{\\text{IN}}^{\\text{AdV}}}",
                      "$\\sigma_{p_{\\text{IN}}^{\\text{CoV}}}",
                      "$\\sigma_{p_{\\text{IN}}^{\\text{MPV}}}",
                      "$\\sigma_{p_{\\text{IN}}^{\\text{PIV}}}")) %>%
  dplyr::select(variable, mean, `X2.5.`, `X97.5.`, Rhat, `n_eff`) %>%
  mutate(across(c(mean, `X2.5.`, `X97.5.`, Rhat), function(x) tex_sign(round_k(x))),
         `n_eff` = round(`n_eff`)) %>%
  as.matrix()

### 2023-06-20 analysis/mol_analysis.Rmd
minor update line list data
fix line list mol
minor update of results

```{r}
line_list_dat <- df_ll %>%
  as.matrix() %>%
  xtable::xtable()

@@

```{r}
# lag types
lag_types <- c("None",
               "1 test date",
               "1 week")

>>>>

```{r}
line_list_dat <- df_ll %>%
  mutate(weekday = weekdays(date)) %>%
  dplyr::select(class, date, weekday, result, virus) %>%
  arrange(class, date) %>%
  as.matrix() %>%
  xtable::xtable()

@@

```{r}
# lag types
lag_types <- c("None",
               "1 test date",
               "1 test week")
